Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-08-20 main.tex
slowly progressing, now finish proofreading Sec 3.3

@@

In this work, we use the \code{Wide} layer data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey. It covers $\sim 300\ \rm{deg}^2$ in all five bands, being 1.5 times larger than the data set (\code{S16A}) analyzed in \citet{Greco2018}. One of the key improvements made in PDR2 is the sky background subtraction. Compared with previous data releases, PDR2 adopted a full focal plane sky subtraction algorithm to overcome the over-subtraction of the local sky background around bright objects \citep{Aihara2018,Li2021}. The unprecedented depth and careful sky subtraction make PDR2 an ideal data set to study low surface brightness galaxies.

@@

\subsubsection{Source Extraction}
We use \code{Source Extractor} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise. This step remains largely the same as in \citetalias{Greco2018}. The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}. We take a mesh size of $43\arcsec$ (doubles the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background. We also require the object to contain at least 100 contiguous pixels to further remove small compact objects. We perform the detection in the $g$-band, but require that all sources are also detected in the $r$-band to exclude spurious detection and artifacts.

@@

\vspace{2em}
After these steps, we have an initial sample that contains 86,002 LSBG candidates. We obtain four times more sources per square degree than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction,  our detection is more inclusive for larger objects, and our size cut is less restrictive for small objects. Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirri, blended compact sources, etc. Therefore, we perform an extra ``deblending'' step to further remove false positives.

\subsection{Deblending}\label{sec:deblending}
A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies. Our initial detection cannot distinguish them from the real LSBGs. In order to identify and remove these objects from our sample, we perform non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}. \code{Scarlet} is a deblending and modeling tool designed for multi-band imaging data. It utilizes the color and morphology information to separate blended objects. In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018} and the online documentation for more details.

@@

Similar to many other modeling codes (e.g., \code{galfit}, \code{imfit}), \code{scarlet} is initialized with positions of detected peaks in the prior steps. The models are then optimized subject to the constraints. Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude blended objects from our sample. In the following subsections, we describe our peak detection, model initialization, and measurement procedures.

\subsubsection{Peak detection}\label{sec:peak}
We generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candidate in our initial sample. We then construct a detection image by taking an average of the four bands weighted by the inverse variance of each band. This detection image is considered to be deeper than the single-band images. 
Next, we run \code{sep} on the detection image using a threshold of 4$\sigma$ above the sky, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels. This step identifies relatively extended sources in the detection image. However, there are still faint and compact peaks not detected. We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components. Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels. This step detects many compact sources that were not included in the previous step. In the end, we combine the two detection catalogs.

@@

\begin{figure*}
	\vbox{
		\centering
		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
	}
	\caption{The distribution of LSBG candidates from our initial sample in the parameter space as measured from the \code{scarlet} models. We visually inspected 5,000 LSBG candidates and labeled them as \code{candy} (LSBGs with typically dwarf galaxy features), \code{galaxy} (higher surface brightness galaxies or galaxies with spiral galaxy features), and \code{junk} (false positives). We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives. After such cuts (bottom panels), 97\% of false positives and 75\% of non-LSB galaxies are removed according to our visual inspection results. 
	}
	\label{fig:deblending_cuts}
\end{figure*}

After running the vanilla scarlet for LSGB candidates, we successfully deblend the target object from nearby sources. We take out the model of the target object (as shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}) and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}. The purpose of this analysis is to extract the structural and morphological parameters of the target object. We further use these diagnostics to remove false positives.

@@

We use these visual inspection results to teach us how to use the morphological and structural diagnostics. The distributions of \code{candy} (blue), \code{galaxy} (green), and \code{junk} (red) in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}. False positives (\code{junk}) are highlighted in red. Although \code{junk} is scattered throughout the parameter space, a large fraction of the junk comprises small things with extreme colors that have small size and very faint surface brightness, large concentration and large asymmetry. Therefore, we come up with the following selection cuts to remove the false positives:
\begin{itemize}
    \item Color:
    \[0.0 < g-i < 1.2,\quad |(g-r) - 0.7\cdot (g-i)| < 0.25\]
    \item Size: \[1.8 \arcsec < r_e < 12 \arcsec\]
    \item Surface brightness: \[\mu_0(g) > 22.5,\quad 23.0 < \mu_{\rm eff}(g) < 27.5,\]
    \item Morphology: 
    \begin{gather*}
        \varepsilon < 0.65,\quad \mathrm{Gini} < 0.70,\quad M_{20} < -1.1,\\
        \mathrm{Gini} < -0.136\cdot M_{20} + 0.37,\\
        1.8 < C < 3.5,\quad A < 0.8.
    \end{gather*}
\end{itemize}
These criteria (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove objects that are not likely to be LSBGs of interest. The color cuts here are narrower than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and background high redshift galaxies. We not only remove objects with small sizes, but also exclude objects with large size, very low surface brightness, and high concentration. This is because the scarlet models of some junk can be very concentrated in the center but also very extended. The slant demarcation line on the Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to separate merging galaxies from normal galaxies.

The bottom panels in Figure \ref{fig:deblending_cuts} show the objects after applying the above selections. With these cuts, 97\% of the false positives are removed, but the majority (70\%) of \code{candy} still remains. The number of \code{galaxy} also drops by 75\%. This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample. But everything comes with a price. Thess cuts sacrifice the completeness of real LSBGs. In Section \ref{sec:completeness}, we characterize the completeness of this ``deblending'' cuts by injecting mock \sersic{} galaxies. \jiaxuan{say our completeness is still high. }

We emphasize that the vanilla scarlet modeling and non-parametric measurements are not designed to recover the intrinsic properties of the galaxies. They are only used as a diagnostic tool to remove false positives. In fact, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects because the faint outskirts are typically not modeled well due to the non-parametric nature of vanilla scarlet and the monotonicity constraint. In the following section, we propose a method to better measure the size and total magnitude of LSBG for science.

\jiaxuan{Compare with smudges and des, discuss why not ML.}

\subsection{Modeling}\label{sec:modeling}
Although vanilla scarlet does a good job at removing false positives, the measured size, magnitude, and surface brightness on the vanilla scarlet model are quite biased. These measurements cannot be used to derive the physical properties of LSBGs.

The non-parametric modeling in \code{scarlet} assumes weak correlation between pixels by imposing the monotonicity constraint. This leads to two problems when applying vanilla scarlet to the LSBGs. First, since pixels are not strongly correlated in the model, the model cannot capture the galaxy light at very low signal-to-noise ratio. Second, the monotonicity constraint stops the model to grow in certain directions if there is another source along this direction, otherwise the monotonicity is broken. This issue, dubbed the ``cookie-cutter effect'', can be seen in Figure \ref{fig:vanilla_scarlet_demo}. As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements.

On the other side, parametric modeling imposes a very strong correlation on pixels. For example, using a 1-D light profile such as \sersic{}, pixels within an isophote are assumed to have the same intensity. Therefore, the signal-to-noise ratio in the outskirts is boosted by effectively combing the information from many pixels. The parametric model also does not suffer from the ``cookie-cutter'' issue.

A traditional way of doing parametric modeling is to first mask out contaminants based on the detection segmentation map, then fit a model to the masked image. However, the fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018}. A possible solution to this problem is to model all the objects in the cutout simultaneously using parametric models (e.g., in DECaLS, \citealt{Dey2019}). In this work, we combine the advantage of parametric modeling with the power of deblending in \code{scarlet}. To be specific, we follow the spirit of deblending as described in Section \ref{sec:deblending}, but replace the non-parametric model for the target with a parametric model. In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized.

We use the Spergel light profile to model the LSBGs. The Spergel profile is motivated by having a simple analytical expression in Fourier space, making it easy to be convolved with a PSF.\footnote{On the opposite, the \sersic{} profile does not have a simple analytic form in Fourier space.} The surface brightness of a Spergel profile \citep{Spergel2010} has a form of
\begin{equation}
    \label{eq:spergel}
    I_\nu(r) = \frac{c_{\nu}^{2} L_{0}}{2\pi r_{0}^{2}} f_{\nu}\left(\frac{c_{\nu} r}{r_{0}}\right),
\end{equation}
where 
\begin{equation}
    f_{\nu}(u)=\left(\frac{u}{2}\right)^{\nu} \frac{K_{\nu}(u)}{\Gamma(\nu+1)},
\end{equation}
and $K_\nu(u)$ is the Modified Bessel function of the second kind. The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfyies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$. Similar to the \sersic{} index, the parameter $\nu$ (Spergel index) controls the concentration of the light profile. As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is interested to the study of LSBGs.

There are several changes in the modeling compared to the deblending step. First, we intialize a vanilla scarlet model for the target object as in Section \ref{sec:deblending}. Then we measure the half-light radius, total flux, and shape of the scarlet model. We use these numbers to initialize the Spergel profile. The size of the bounding box is also updated to be the maximum between 250 pixel and $10\, r_e$. Objects within this bounding box are included in the modeling, but only the target object is modeled by the Spergel profile. For the target, we still requires positivity constraint, as the mononicity is automatically satisfied.

After optimization, we take the $r_0$ in Equation \eqref{eq:spergel} as the circularized half-light radius $r_e$, and take the $L_0$ as the total flux. The average surface brightness $\overline{\mu}_{\rm eff}$ is calculated in the same way as in Section \ref{sec:non-par-measurement}.

We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27$ is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

\subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}

\subsubsection{Completeness}\label{sec:completeness}
\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{completeness.pdf}
	}
	\caption{Caption}
	\label{fig:completeness}
\end{figure*}

%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
After the source detection step and the deblending step, we obtain a sample of LSBG candidates where the fraction of false positives is very small.

It is crucial to characterize the completeness of both detection and deblending in order to understand our survey efficiency and the properties of the LSBG population. We performed a large suite of image simulation to derive the completeness. The overall completeness is a combination of detection and deblending completenesses. The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after cuts.

For the detection completeness, we inject $\sim 35,000$ (check number with Johnny) mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline. This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}. However, we find no noticable difference between this method and the direct injection to coadd images.}. The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \epsilon < 0.6$), resembling the LSBG distribution in \citetalias{Greco2018}. They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$) and red ($g-i=0.82,\ g-r=0.56$) color with equal chance.

We find the detection completeness mainly depends the size and surface brightness of mock galaxy. As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes. It drops below 50\% when the surface brightness gets fainter than 27.5 mag arcsec$^{-2}$. We find negligible dependendce of completeness on \sersic{} index, color, and additional structure of galaxy (such as star-forming clumps). However, we find the completeness declines above ellipticity $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample. In this work, we neglect the dependences of detection completeness on parameters other than size and surface brightness.

% \textbf{Need to update the completeness to the S18A version. Ping Johnny.}

For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them. The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$. Following the procedure described in Sec \ref{sec:deblending}, we measure the non-parametric sizes and surface brightnesses on the scarlet models of the mock galaxies. The deblending completeness is shown in the middel panel of Figure \ref{fig:completeness}. The deblending completeness is high at bright surface brightnesses, but starts to decline with increasing size and surface brightness. Mock galaxies fainter than $\overline{\mu}_{\rm eff}(g) > 27.5$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy. The deblending step is very effective on removing false positives, but at a cost of losing very LSB galaxies.

The combined completeness is shown in the right panel of Figure \ref{fig:completeness}. The countours shows the 70\%, 50\%, and 20\% completenesses, respectively. \textbf{Also compare our completeness with other surveys.}

%\textbf{Make sure that completeness is assigned based on the bias-corrected size and SB.} Checked. No problem.

\subsubsection{Measurement uncertainty}\label{sec:meas_unc}
We characterize the quality of the Spergel modeling by injecting mock \sersic{} galaxies into the cutout and compare the recovered properties with the truth, as shown in Appendix \ref{sec:meas_unc}. Overall speaking, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ is under-estiamted. We also characterize the bias and the scatter in measurement as a function of size and surface brightness. We apply the bias correction to the measurement of LSBGs, and incorporate the measurement error into the science figures.

>>>>

This paper is framed as follows. We detect LSBGs, then match them to MW analogs such that we can assume distances.

@@

In this work, we use the \code{Wide} layer coadd data from the Public Data Release 2 (PDR2, also known as \code{S18A}, \citealt{Aihara2018}) of the HSC survey. It covers $\sim 300\ \rm{deg}^2$ in all five bands, being 1.5 times larger than the data set (\code{S16A}) analyzed in \citet{Greco2018}. One of the key improvements made in PDR2 is the sky background subtraction. Compared with previous data releases, PDR2 adopted a full focal plane sky subtraction algorithm to overcome the over-subtraction of the local sky background around bright objects \citep{Aihara2018,Li2021}. The unprecedented depth and careful sky subtraction make PDR2 an ideal data set to study low surface brightness galaxies.

@@

\subsubsection{Source Extraction}
We use \href{https://www.astromatic.net/software/sextractor/}{\code{Source Extractor}} \citep{Bertin1996} to detect sources on the ``cleaned'' images where the bright sources and small compact sources are replaced by sky noise. This step remains largely the same as in \citetalias{Greco2018}. The images are convolved with a Gaussian kernel of FWHM=$1\arcsec$ to maximize the contrast between LSBGs and sky background \citep[e.g.,][]{Irwin1985,Akhlaghi2015,Greco2018}. We take a mesh size of $43\arcsec$ (doubles the mesh size used in \citetalias{Greco2018} to allow bigger galaxies in our sample) to measure the local background and detect objects that are 0.7$\sigma$ per pixel above the local sky background. We also require the object to contain at least 100 contiguous pixels to further remove small compact objects. We perform the detection in the $g$-band, but require that all sources are also detected in the $r$-band to exclude spurious detection and artifacts.

@@

\vspace{2em}
After these steps, we have an initial sample that contains 86,002 LSBG candidates. We obtain four times more sources per square degree ($\sim 280\ \mathrm{deg}^{-2}$) than \citetalias{Greco2018} mainly because PDR2 has a better sky subtraction,  our detection is more inclusive for larger objects, and our size cut is less restrictive for small objects. Among these objects, there are still a lot of false positives, including shredded galaxy outskirts, tidal features, Galactic cirri, blended compact sources, etc. Therefore, we perform an extra ``deblending'' step to further remove false positives.

\subsection{Deblending}\label{sec:deblending}
Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG search \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}. A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies. Our initial detection cannot distinguish them from the real LSBGs. In order to identify and remove these objects from our sample, we perform non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}. \code{Scarlet} is a deblending and modeling tool designed for multi-band imaging data. It utilizes the color and morphology information to separate blended objects. In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation for more details.

@@

Similar to many other modeling codes (e.g., \code{galfit} \citealt{galfit}, \code{imfit} \citealt{imfit}), \code{scarlet} is initialized with positions of detected peaks in the prior steps. The models are then optimized subject to the constraints. Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude blended objects from our sample. In the following subsections, we describe our peak detection, model initialization, and measurement procedures.

\subsubsection{Peak detection}\label{sec:peak}
We generate cutout images with a size of $1\arcmin$ in $griz$-bands for each LSBG candidate in our initial sample. We then construct a detection image by taking an average of the four bands weighted by the inverse variance of each band. This detection image is considered to be deeper than the single-band images. 
Next, we run \code{sep} on the detection image using a threshold of 4$\sigma$ above the sky, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels. This step identifies relatively extended sources in the detection image. However, there are still faint and compact peaks not detected. We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering). Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels. This step detects many compact sources that were not included in the previous step. In the end, we combine the two detection catalogs.

@@

\begin{figure*}
	\vbox{
		\centering
		\includegraphics[width=1.0\linewidth]{deblending_cuts.pdf}
	}
	\caption{The distribution of LSBG candidates from our initial sample in the parameter space as measured from the \code{scarlet} models. We visually inspected 5,000 LSBG candidates and labeled them as \code{candy} (LSBGs with typically dwarf galaxy features), \code{galaxy} (higher surface brightness galaxies or galaxies with spiral galaxy features), and \code{junk} (false positives). We propose a selection based on size, color, surface brightness and morphology (dashed boxes) to effectively remove false positives but still achieves a high completeness. After such cuts (bottom panels), 97\% of false positives and 75\% of non-LSB galaxies are removed according to our visual inspection results. 
	}
	\label{fig:deblending_cuts}
\end{figure*}

After running the vanilla scarlet for LSGB candidates, we successfully deblend the target object from nearby sources. Unlike other modeling codes, the non-parametric \code{scarlet} model is very flexible on modeling galaxies with complex structures. But the non-parametric nature means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model. As shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}, we take out the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}. The purpose of this analysis is to extract the structural and morphological parameters of the target object. We further use these diagnostics to remove false positives.

@@

We use these visual inspection results to teach us how to use the morphological and structural diagnostics. The distributions of \code{candy} (blue), \code{galaxy} (green), and \code{junk} (red) in the parameter space are shown in the top panels of Figure \ref{fig:deblending_cuts}. Although \code{junk} is scattered throughout the parameter space, a large fraction of the junk comprises small things with very red colors, very faint surface brightness, large concentration and large asymmetry. Therefore, we come up with the following selection cuts to remove the false positives:
\begin{itemize}
    \item Color:
    \[0.0 < g-i < 1.2,\quad |(g-r) - 0.7\cdot (g-i)| < 0.25\]
    \item Size: \[1.8 \arcsec < r_e < 12 \arcsec\]
    \item Surface brightness: \[\mu_0(g) > 22.5,\quad 23.0 < \mu_{\rm eff}(g) < 27.5,\]
    \item Morphology: 
    \begin{gather*}
        \varepsilon < 0.65,\quad \mathrm{Gini} < 0.70,\quad M_{20} < -1.1,\\
        \mathrm{Gini} < -0.136\cdot M_{20} + 0.37,\\
        1.8 < C < 3.5,\quad A < 0.8.
    \end{gather*}
\end{itemize}
These criteria (shown as dashed lines in Figure \ref{fig:deblending_cuts}) effectively help us remove objects that are not likely to be LSBGs of interest. The color cuts here are narrower than the one used in the initial detection (Sec \ref{sec:detection}) to further remove junk and background high redshift galaxies. We not only remove objects with small sizes, but also exclude objects with large size, very low surface brightness, and high concentration. This is because the scarlet models of some junk can be very concentrated in the center but also very extended. The slant demarcation line on the Gini-$M_{20}$ diagram is motivated by the line used in \citet{Lotz2008} to separate merging galaxies from normal galaxies.

The bottom panels in Figure \ref{fig:deblending_cuts} show the objects after applying the above selections. With these cuts, 97\% of the false positives are removed, but the majority (70\%) of \code{candy} still remains. The number of \code{galaxy} also drops by 75\%. This empirical selection based on the non-parametric measurements on the scarlet models successfully removes most of the false positives and a large fraction of background galaxies in our initial sample. Furthermore, the completeness of real LSBG detection remains high. In Section \ref{sec:completeness}, we characterize the completeness of this ``deblending'' step by injecting mock \sersic{} galaxies, and we achieve $\sim80\%$ completeness at $\sbeff = 27.0\ \sbunit$ and $>50\%$ completeness at $\sbeff = 27.5\ \sbunit$ (Fig. \ref{fig:completeness}). We emphasize that the vanilla scarlet modeling and non-parametric measurements are not designed to recover the intrinsic properties of the galaxies. They are used only as a diagnostic tool to remove false positives. We perform more detailed modeling in Section \ref{sec:modeling} to measure galaxy properties for science.

We notice that many other works have been using machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection. Among others, \citet{Tanoglidis2021} take the output catalog from \code{Source Extractor} and use the Support Vector Machine algorithm to classify objects in their initial sample and reduce the number of objects that are visually inspected. \citet{Zaritsky2019,Zaritsky2021,Zaritsky2022} use convolutional neural networks to classify LSBGs into binary classes based on their images. These endeavors certainly help reducing the human labor on visually inspecting tens of thousands of objects. However, training such a supervised ML algorithm relies on the labeled data which should also sample the parameter space evenly. Once labels are assigned (e.g., LSBG v.s. non-LSBG), there will be little way to change later. On the contrary, our cuts based on the measured properties can be tweaked to be more complete (including more junks) or be more pure (aggressive cuts) depends on the specific science goal. The visual inspections only guide us to design those metrics. This measurement-based method is more intuitive, reproducible, and transferable. We will also explore machine learning methods and compare with our deblending cuts in future works. We would also like to utilize the information about the Milky Way dust to exclude spurious detection on Galactic cirrus \citep{Zaritsky2021,Zaritsky2022}.

% Tanoglidis doesn't estimate measurement uncertainty. Doesn't systematically estimate completeness, only validates the comp using deeper fornax observations. Also, the artifact of HSC is less compared with DES/DECaLS?
% SMUDGES: Their sample might be cleaner thanks to their wavelet detection emphasizing specific spatial frequency. But they still need a lot of visual inspection.

\subsection{Modeling}\label{sec:modeling}
Although the vanilla scarlet modeling provides useful information to help us remove false positives, it does not necessarily give us unbiased estimations on size, color, total magnitude, etc. In fact, the vanilla scarlet model usually under-estimates the size and the total flux of LSB objects. This is because the faint outskirts of LSBGs are typically not modeled well due to the non-parametric nature of vanilla scarlet. We elaborate this point as follows.

When doing parametric modeling such as \sersic{} fitting, we effectively apply radial averaging within elliptical annulus and boost the SNR by binning pixels. In other words, pixels within the same isophotal annulus are assumed to have the same intensity thus are strongly correlated. However, the non-parametric nature of vanilla \code{scarlet} only assumes monotonicity, which imposes quite weak correlation among pixels. Consequently, it is very hard to for the non-parametric modeling to probe down to very low surface brightness features. Furthermore, the monotonicity constraint stops the model to grow in certain directions if there is another source along this direction, otherwise the monotonicity is broken. This issue, dubbed the ``cookie-cutter effect'', can be seen in the third column of Figure \ref{fig:vanilla_scarlet_demo} where the model for target object never exceeds the other objects next to it. As a result, the non-parametric model often does not capture the LSB outskirts of LSBG, thus biasing the measurements. In the following, we explore a novel method to perform parametric fitting while combing the advantage of \code{scarlet}.

A traditional way of doing parametric modeling is to first mask out contaminants based on the detection segmentation map, then fit a model to the masked image. However, the fitting results are very sensitive to the masking scheme \citep[e.g.,][]{Greco2018} and sky background. A possible solution to this problem is to simultaneously model all the objects in the cutout and the sky using parametric models (e.g., in DECaLS, \citealt{Dey2019}). In this work, we combine the advantage of parametric modeling with the power of deblending in \code{scarlet}. To be specific, we follow the spirit of deblending as described in Section \ref{sec:deblending}, but replace the non-parametric model for the target with a parametric model. In this way, the LSB outskirts of LSBGs can be better captured with the parametric model and the impact of contaminants is minimized because they are modeled simultaneously. The parametric model for the target object does not suffer from the ``cookie-cutter'' issue any more.

We use the Spergel surface brightness profile \citep{Spergel2010} to model the LSBGs. The Spergel profile is motivated by having a simple analytical expression in the Fourier space, making it easy to be convolved with a PSF\footnote{On the opposite, the \sersic{} profile does not have a simple analytic form in the Fourier space.}. The surface brightness of a Spergel profile has a form of
\begin{equation}
    \label{eq:spergel}
    I_\nu(r) = \frac{c_{\nu}^{2} L_{0}}{2\pi r_{0}^{2}} f_{\nu}\left(\frac{c_{\nu} r}{r_{0}}\right),
\end{equation}
where 
\begin{equation}
    f_{\nu}(u)=\left(\frac{u}{2}\right)^{\nu} \frac{K_{\nu}(u)}{\Gamma(\nu+1)},
\end{equation}
and $K_\nu(u)$ is the Modified Bessel function of the second kind. The half-light radius is $r_0$, the total luminosity is $L_0$, and $c_\nu$ satisfies the equation $(1 + \nu)f_{\nu + 1}(c_\nu) = 1/4$. Similar to the \sersic{} index, the parameter $\nu$ (dubbed as ``Spergel index'') controls the concentration of the light profile. As shown in Appendix \ref{ap:spergel}, the Spergel profile approximates the \sersic{} profile very well over the range of \sersic{} index that is interested to the study of LSBGs.

We initialize the Spergel model for the target object differently, while other objects are still initialized in the same way as in the deblending step (Section \ref{sec:deblending}). First, we initialize a vanilla scarlet model for the target object, and we measure the effective radius $r_e$, total flux, and the shape of the scarlet model. We use these numbers to initialize the Spergel profile. The size of the bounding box is also updated to be the maximum between 250 pixels and $10\, r_e$. Peaks within this bounding box (other than the target) are modeled using vanilla scarlet. For the target, we still requires positivity constraint, and the monotonicity is automatically satisfied by the Spergel profile.

After optimization, we take the $r_0$ in Equation \eqref{eq:spergel} as the circularized half-light radius $r_e$, and take the $L_0$ as the total flux. The average surface brightness $\overline{\mu}_{\rm eff}$ is calculated in the same way as in Section \ref{sec:non-par-measurement}. In the following section, we assess the quality of the Spergel modeling by injecting mock \sersic{} galaxies and compare recovered properties with truth.

\subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
The completeness of the LSBG search is important not only for understanding our searching efficiency and improving the method in the future but also for deriving the completeness-corrected results for LSBG sciences. Similar to many other works \citep[e.g.,][]{Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and try to recover them from the image. Using these mock galaxies, we also characterize the measurement bias and uncertainty by comparing the measured properties with the truth.

\subsubsection{Completeness}\label{sec:completeness}
%Since the scarlet model is PSF-deconvolved, the color is not affected by the seeing differences among bands. 
A real LSBG can be missed in the detection step (Sec. \ref{sec:detection}) or be excluded in the deblending step (Sec. \ref{sec:deblending}). Thus, the overall completeness is a combination of detection completeness and deblending completeness. We performed a large suite of image simulation to derive the completeness. The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remained after the deblending cuts.

For the detection completeness, we inject $\sim 700,000$ mock galaxies with single \sersic{} light profiles \citep{Sersic1963} into the coadd images\footnote{We have also done extensive tests on injecting mock galaxies to the raw images and going through the entire data reduction pipeline. This is very expensive in terms of both CPU time and disk space, since we must run the full \code{hscPipe}. However, we find no noticeable difference on the completeness between this method and the direct injection to coadd images.}. The mock galaxies follow uniform distributions in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$), surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$), \sersic{} index ($0.8 < n < 1.2$), and ellipticity ($0 < \varepsilon < 0.6$) by resembling the LSBG distribution in \citetalias{Greco2018}. They are randomly assigned to have a blue ($g-i=0.47,\ g-r=0.32$), medium ($g-i=0.64,\ g-r=0.43$), and red ($g-i=0.82,\ g-r=0.56$) color with equal chance. Then we run the detection step as described in Sec. \ref{sec:detection} and cross-match the detection catalog with the input mock galaxy catalog to calculate completeness.

We find that the detection completeness mainly depends on the size and surface brightness. As shown in the left panel of Figure \ref{fig:completeness}, the detection completeness remains high across different sizes. It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$. We find negligible dependence of completeness on \sersic{} index, color, and ellipticity. Therefore, we neglect the dependence of detection completeness on parameters other than size and surface brightness hereafter.\footnote{We performed a smaller set of image simulation where we extend the ellipticity range and also simulated galaxies with additional structures (such as star-forming clumps). We find the completeness declines for $\varepsilon > 0.6$, suggesting that edge-on disk galaxies may be missing from our sample. Please see \citet{Greene2022} for more details.}

For the deblending completeness, we inject 5,000 mock \sersic{} galaxies into the coadd and run vanilla scarlet on them. The mock galaxies follow the same uniform distribution in size, surface brightness, ellipticity, \sersic{} index as for deriving the detection completeness, but follow a Gaussian distribution in color: $g-i \sim \mathcal{N}(0.6, 0.2^2),\ g-r = 0.7 (g-i) + \mathcal{N}(0, 0.03^2)$. We measure the size and surface brightness on the scarlet models of the mock galaxies, then we apply the deblending cuts. The deblending completeness as a function of size and surface brightness is shown in the middle panel of Figure \ref{fig:completeness}. The deblending completeness is very high at the bright end, but starts to decline with increasing size and surface brightness. Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy. Interestingly, the detection completeness and deblending completeness all drop below 40\% around $\sbeff=27.5\ \sbunit$. In this sense, the detection and deblending cooperate well in terms of completeness.

The combined completeness is shown in the right panel of Figure \ref{fig:completeness}. The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$. The completeness drops as we go to fainter surface brightness and smaller size.

Compare with vdb17, carlsten22, smudges21/22, tanoglidis21.

Our high completeness demonstrates the power of HSC images on LSBG studies.

\jiaxuan{Also compare our completeness with other surveys.}
